Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-22 paper.tex

\item \textit{Fragmented} (``frag'' for short). This workload first allocates
$2^{20}$ contiguous 4KB blocks. Then, it resizes every other block to
16KB. This represents the worst case behavior we could think of. It requires the
kernel to find a block it has not touched in $2^{20}$ operations and move
it somewhere else.  
\end{itemize}

>>>>

\item \textit{Fragmented} (``frag'' for short). This workload first allocates
    $4^{20}$ contiguous 4KB blocks. Then, it resizes every other block to 16KB.
        The resizing operation, rather than the initial allocation is measured.
\end{itemize}
